Increased productivity using Atomify - a real-time LAMMPS visualizer

### 2018-06-03 ms.tex
Some more?

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{lj_flow/configuration.png}
	\caption{
		Initial configuration in our case study simulation.
		A periodic box consisting of $(40\times20\times20)$ FCC unit cells with reduced density $\rho^* = 0.8442$ where we will have gas flow in a cylinder of 5 unit cell radius.
		The different colors indicate the regions of which different integration rules apply.
		\textcolor{atomify-blue}{Blue} atoms are fixed and do not move at all,
		whereas the \textcolor{atomify-yellow}{yellow} atoms are thermalized with a Langevin\citep{schneider1978molecular} dissipative thermostat to mimick the heat exchange with the frozen bulk atoms.
		The \textcolor{atomify-red}{red} and the \textcolor{atomify-green}{green} atoms are integrated normally, except the \textcolor{atomify-green}{green} atoms (gas atoms) have an applied constant acceleration representing the pressure gradient.
		Setting up and verifying this system is simple using Atomify due to the real-time coloring of groups and regions.
    }
	\label{fig:cylinder_simulation}
\end{figure}

In this case study, we will use Atomify to measure the velocity profile of a Lennard Jones gas with varying density to observe the slip velocity effect at low densities.
We will create a nanotube inside a Lennard Jones solid of size  $(40\times20\times20)$ unit cells, reduced density $\rho^* = 0.8442$, where the fluid will flow due to an induced pressure gradient, see figure \ref{fig:cylinder_simulation}.
Here we apply a pressure gradient $\nabla P$ in the $x$-direction on the gas atoms using a constant acceleration $a$
\begin{align}
	a = \frac{\nabla P}{\rho_m},
\end{align}
where $\rho_m$ is the mass density of the gas atoms.
Applying such an acceleration means adding energy to the system which in turn will increase the temperature and eventually melt the system.
We want to couple the solid to an external heat bath so the added energy can be transferred out through a thermostat.
Even though we only apply a pressure gradient on the gas atoms, this induced momentum will also be transferred to the solid atoms which eventually will start moving in the positive $x$-direction which is not desired.
We therefore freeze the outmost atoms.
To achieve these properties of the system, the atoms are divided into multiple regions, which are integrated differently:

@@

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{lj_flow/configuration.png}
	\caption{
		Initial configuration in our case study simulation.
		A periodic box consisting of $(40\times20\times20)$ FCC unit cells with reduced density $\rho^* = 0.8442$ where we will have gas flow in a cylinder of 5 unit cell radius.
		The different colors indicate the regions of which different integration rules apply.
		\textcolor{atomify-blue}{Blue} atoms are fixed and do not move at all,
		whereas the \textcolor{atomify-yellow}{yellow} atoms are thermalized with a Langevin\citep{schneider1978molecular} dissipative thermostat to mimick the heat exchange with the frozen bulk atoms.
		The \textcolor{atomify-red}{red} and the \textcolor{atomify-green}{green} atoms are integrated normally, except the \textcolor{atomify-green}{green} gas atoms have an applied constant acceleration representing the pressure gradient.
		Setting up and verifying this system is simple using Atomify due to the real-time coloring of groups and regions.
    }
	\label{fig:cylinder_simulation}
\end{figure}

In this case study, we will use Atomify to measure the velocity profile of a Lennard Jones gas with varying density to observe the slip velocity effect at low densities.
We will create a nanotube inside a Lennard Jones solid of size  $(40\times20\times20)$ unit cells, reduced density $\rho^* = 0.8442$, where the fluid will flow due to an induced pressure gradient, see figure \ref{fig:cylinder_simulation}.
Here we apply a pressure gradient $\nabla P$ in the $x$-direction on the gas atoms using a constant acceleration $a$ calculated as
\begin{align}
	a = \frac{\nabla P}{\rho_m},
\end{align}
where $\rho_m$ is the mass density of the gas atoms.
Applying such an acceleration means adding energy to the system which in turn will increase the temperature and eventually melt the system.
We want to couple the solid to an external heat bath so the added energy can be transferred out through a thermostat.
Even though we only apply a pressure gradient on the gas atoms, this induced momentum will also be transferred to the solid atoms which eventually will start moving in the positive $x$-direction which is not desired.
We therefore freeze the outmost atoms.
To achieve these properties of the system, the atoms are divided into multiple regions, which are integrated differently:

@@

\subsection{Creating the initial geometry}
We create a new script in Atomify using \keys{\cmd+R}, and save it (\keys{\cmd+S}) as \code{run.in}.
Starting from the input script in listing \ref{lst:simple.in}, we modify it to create a larger simulation box with $(40\times20\times20)$ unit cells.
Then, to define the inner cylinder, we first specify the radius and the center before the region command:
\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
	variable R equal $(ly*0.25)
	variable c equal $(ly*0.5)
	region cylinder1 cylinder x $c $c $R EDGE EDGE
\end{lstlisting}
which gives
